### 2022-03-21 chapters/04-chapter-4.tex
txs auto checkin

Algoritma pertama yang akan dijabarkan adalah algoritma proses umum yang terjadi pada sistem PRA. Algoritma ini akan dijalankan sebagai program utama di sistem PRA.
\begin{algorithm}
\caption{Algoritma \textit{main}}\label{alg-main}
	\If{baseline model not exist}{get baseline model}

\end{algorithm}

>>>>

Algoritma pertama yang akan dijabarkan adalah algoritma proses umum yang terjadi pada sistem PRA. Algoritma ini akan dijalankan sebagai program utama di sistem PRA.
\begin{algorithm}[hbt!]
	\SetAlgorithmName{Algoritme}{Algoritme}

\If(\tcc*[h]{a simple if but with a comment on the same line}){this is true}{
	we do that, else nothing\;
	\tcc{we will include other if so you can see this is possible}
	\eIf{we agree that}{
		we do that\;
	}{
		else we will do a more complicated if using else if\;
		\uIf{this first condition is true}{
			we do that\;
		}
		\uElseIf{this other condition is true}{
			this is done\tcc*[r]{else if}
		}
		\Else{
			in other case, we do this\tcc*[r]{else}
		}
	}
}

%	\KwData{Write here the required data}
%	\KwResult{Write here the expected result}
%	initialization\;
%	\While{While condition}{
%		instructions\;
%		\eIf{condition}{
%			instructions1\;
%			instructions2\;
%		}{
%			instructions3\;
%		}
%	}
	\caption{Algoritme program \textit{main}}\label{alg:main}
\end{algorithm}

\begin{algorithm}[hbt!]
	\SetAlgorithmName{Algoritme}{Algoritme}

	\caption{Algoritme pengambilan data \textit{baseline}}\label{alg:baseline-ret}
\end{algorithm}

Algoritme selanjutnya akan menjelaskan
